Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-06-13 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
mat graph def

\textcolor{red}{Suggested revision:}
(Materialization Graph).
A \emph{materialization graph}, with respect to
a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
denoted by $\mathcal{G}=\langle V, E\rangle$ where,
\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
\end{enumerate}
For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are two nodes,
we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
of $v_1$.

Further, for each $H,B_1,\ldots,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
  \item if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
  $B_1,\ldots,B_n$ are all the parents of $H$, then $B_1,\ldots,B_n\rightarrow H\in P^*$;
  \item if $H$ has an in-degree of $0$, then $H$ is an original fact
    of $P$.
\end{enumerate}
A materialization graph $\mathcal{G}$ is a \emph{complete materialization graph},
when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
\end{definition}

>>>>

\textcolor{red}{Suggested revision:}
(Materialization Graph).
A \emph{materialization graph}, with respect to
a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
denoted by $\mathcal{G}=\langle V, E\rangle$ where,
\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
  \item $V$ is the node set and $\textbf{I} \subseteq V\subseteq T_R^{\omega}(\textbf{I})$;
  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
\end{enumerate}
For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are two nodes,
we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
of $v_1$. A materialization graph satisfies the following conditions:
\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
\item each $v \in \textbf{I}$, $v$ has an in-degree of $0$;
\item each $H \in V \setminus \textbf{I}$ such that $B_1,\ldots,B_n$
  are all the parents of $H$, there is exactly one
  $B_1,\ldots,B_n\rightarrow H\in P^*$.
\end{enumerate}
A materialization graph $\mathcal{G}$ is a \emph{complete materialization graph},
when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
\end{definition}
